\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{4.1pt}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Uzair Nawaz} \\ \vspace{1pt}
    \small 512-244-3928$|$ \href{mailto:uzair.nawaz@utexas.edu}{\underline{uzair.nawaz@utexas.edu}} $|$ 
    \href{https://github.com/uzairnawaz}{\underline{github.com/uzairnawaz}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Austin}{Austin, TX}
      {B.S. Computer Science Honors (Turing Scholar), GPA: 3.95/4.00}{Graduating Spring 2027}
      \vspace{-2pt}\small{\item
      \begin{tabularx}{0.97\textwidth}{p{1.6cm} X}
        Courses: & Honors Algorithms, Honors Computer Security, Honors Operating Systems, Programming for Performance, Honors Computer Architecture, Data Structures, Linear Algebra, Probability and Statistics, Discrete Math\\
      \end{tabularx}\vspace{-7pt}}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Java, x86/ARM/RISC-V Assembly, Rust, Verilog, Bash, JavaScript, HTML/CSS, SQL} \\
     \textbf{Tools}{: Git, CMake, Makefile, GDB, JIRA, Confluence, Unity Game Engine, Arduino Microcontroller} \\
    }}\vspace{-4pt}
 \end{itemize}
  
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google}{May 2025 -- Aug 2025}
      {Associate Software Developer Intern - Compilers, Runtimes, and Toolchains Team}{Sunnyvale, CA}
      \resumeItemListStart
        \resumeItem{Contributed to LLVM-libc, an open-source standard library for C which is part of The LLVM Project.}
        \resumeItem{Designed, implemented, and tested a system to perform conversion between character encodings in \textbf{C++}.}
        \resumeItem{Contributed to the pthreads implementation, designing a reusable barrier for thread synchronization.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {The University of Texas at Austin}{Jan 2025 -- May 2025}
      {Undergraduate Teaching Assistant (CS 439: Operating Systems)}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Planned, graded, and answered questions related to programming assignments and quizzes for about 65 students.}
    \resumeItemListEnd

    \resumeSubheading
      {Keysight Technologies}{May 2024 -- Aug 2024}
      {Network Visibility Software Intern}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Developed a staged upgrade process for loading new software on network switches. Allowed network switches to remain online for a large part of the software upgrade process, decreasing downtime by about 40\%.}  
        \resumeItem{Reorganized one-shot \textbf{Bash} upgrade scripts into logical stages that could be run independently.}
        \resumeItem{Improved existing web GUI using ExtJS to display software installation status and future actions.} 
        \resumeItem{Implemented new features to \textbf{Java} REST API, allowing users to trigger specific stages of the installation process.} 
      \resumeItemListEnd
      
    \resumeSubheading
      {Institute for Computing in Research}{July 2022 -- Aug 2022}
      {Research Intern}{Austin, TX}
      \resumeItemListStart
      \resumeItem{Worked with a mentor to create an n-body simulation in \textbf{Python} to predict the motion of gravitating particles.}
        \resumeItem{Used matplotlib library to animate simulations either two- or three-dimensionally.}
        \resumeItem{Performed benchmarks and generated plots to compare accuracy/efficiency of algorithms (Barnes-Hut vs $N^2$).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  \vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LDOS ML Compiler Research Project} $|$ \emph{Python, PyTorch, Triton, C, Linux Kernel}}{}
          \resumeItemListStart
          \resumeItem{Developed a process to compile PyTorch models using Triton and perform inference on them within the kernel.}
          \resumeItem{Increased the feasability of using ML-based OS policies instead of the existing heuristic approaches.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Chess Engine} $|$ \emph{C++, Google Test}}{}
          \resumeItemListStart
            \resumeItem{Wrote a UCI-compatible chess engine that applies heuristics and alpha-beta pruning to choose the best move.}
            \resumeItem{Represented the board as a collection of bitboards (64-bit integers with each bit representing a square), computing moves through efficient bitwise operations. Utilized Google Test framework to verify move generation.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Object-Oriented FUN Compiler} $|$ \emph{C++, ARM Assembly, Makefile}}{}
          \resumeItemListStart
            \resumeItem{Built compiler to translate a toy language to ARM assembly. Supports conditionals, loops, functions, and classes.}
            \resumeItem{Implemented compile-time optimizations such as constant folding and tail call elimination by constructing an AST.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Pipelined Processer} $|$ \emph{SystemVerilog}}{}
          \resumeItemListStart
            \resumeItem{Designed a 6-staged pipelined processor with an ISA that included branches, memory read/writes (including misaligned addresses), and arithmetic. Implemented a branch predictor to reduce pipeline flushes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Network Card Driver} $|$ \emph{C++}}{}
          \resumeItemListStart
            \resumeItem{Implemented a driver for the E1000 family of network cards. Supported both transmitting and receiving.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Chip 8 Emulator} $|$ \emph{C++, SFML}}{}
          \resumeItemListStart
            \resumeItem{Created a Chip 8 interpreter. Supports arithmetic, memory read/write, branch, and graphics instructions.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
